Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2016-11-28 ms_pre_post.Rmd
Add Fisher reference somewhere note

---
title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry"
author: "A. Bradley Duthie, Greta Bocedi, Ryan R. Germain, Matthew E. Wolak, and Jane M. Reid"
date: "August 24, 2016"
output:
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
  pdf_document:
    fig_caption: yes
  html_document: default
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 2
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

>>>>

---
title: Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated
  polyandry
author: A. Bradley Duthie, Greta Bocedi, Ryan R. Germain, Matthew E. Wolak, and Jane
  M. Reid
date: "August 24, 2016"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 2
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

<!--- Will most likely need to read and cite \cite{Fisher2016} here (Fisher et al. 2016 Behavioural Ecology -- pre- and post-copulatory competition using network theory --->
